Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-20 paper/aldebaran.tex
candidate title
some references

\title{Something About Ground Based Asteroseismology}

@@

@@

\section{Aldebaran}

>>>>

\title{Detection of Oscillations in Aldebaran with Ground-Based Observations}

@@

Aldebaran, or $\alpha$~Tauri, is one of the brightest and most easily recognized naked-eye stars, and has long been the subject of astronomical investigations.

@@

\section{Aldebaran}
Aldebaran is one of the nearest red giant stars, at a distance of only $19.96 \pm 0.38$~pc \citep{hipparcos}, and its position near the Ecliptic permits the determination of its angular diameter by lunar occultations \citep[$20.58 \pm 0.03$ mas;][]{richichi2005,1979ApJ...228L.111B,brown1979,panek1980}.
